Discriminating the Influence of Correlated Factors \\from Multivariate Observations: the Back-to-Back Regression

### 2020-03-05 paper/paper.tex
fig

\journal{Neuroimage}

@@

\section{Introduction}

\input{introduction.tex}

@@

\begin{figure}[t!]
  \include{fig_problem.tex}
  \label{fig:b2b}
\end{figure}

@@

\input{synthetic.tex}

@@

\input{meg_exps.tex}

>>>>

% \journal{Neuroimage}

@@

\section{Introduction}
\input{introduction.tex}

@@

\begin{figure}[t!]

  \centering
  \begin{tikzpicture}
  \newcommand\posY{0}
  \newcommand\posX{3}
  \newcommand\posE{5}
  \newcommand\posN{7}
  \newcommand\posF{10}

  \node[thick, draw=black, minimum height=3cm, minimum width=2cm, fill=yellow!10] (Y) at (\posY, 0){};
  \node[] (eq) at (1.5, 0){$=$};
  \node[] (times) at (4, 0){$\times$};
  \node[thick, draw=black, minimum height=3cm, minimum width=1cm, fill=yellow!10] (X) at (\posX, 0){};
  \node[thick, draw=black, minimum height=1cm, minimum width=1cm, fill=red!10] (E) at (\posE, 0){};

  \draw[fill=white] (\posE - 0.5 + 0.0, 0.5 - 0.0) rectangle (\posE - 0.5 + 0.0 + 0.1, 0.5 - 0.0 - 0.1);
  \draw[fill=black] (\posE - 0.5 + 0.1, 0.5 - 0.1) rectangle (\posE - 0.5 + 0.1 + 0.1, 0.5 - 0.1 - 0.1);
  \draw[fill=white] (\posE - 0.5 + 0.2, 0.5 - 0.2) rectangle (\posE - 0.5 + 0.2 + 0.1, 0.5 - 0.2 - 0.1);
  \draw[fill=white] (\posE - 0.5 + 0.3, 0.5 - 0.3) rectangle (\posE - 0.5 + 0.3 + 0.1, 0.5 - 0.3 - 0.1);
  \draw[fill=white] (\posE - 0.5 + 0.4, 0.5 - 0.4) rectangle (\posE - 0.5 + 0.4 + 0.1, 0.5 - 0.4 - 0.1);
  \draw[fill=white] (\posE - 0.5 + 0.5, 0.5 - 0.5) rectangle (\posE - 0.5 + 0.5 + 0.1, 0.5 - 0.5 - 0.1);
  \draw[fill=white] (\posE - 0.5 + 0.6, 0.5 - 0.6) rectangle (\posE - 0.5 + 0.6 + 0.1, 0.5 - 0.6 - 0.1);
  \draw[fill=black] (\posE - 0.5 + 0.7, 0.5 - 0.7) rectangle (\posE - 0.5 + 0.7 + 0.1, 0.5 - 0.7 - 0.1);
  \draw[fill=white] (\posE - 0.5 + 0.8, 0.5 - 0.8) rectangle (\posE - 0.5 + 0.8 + 0.1, 0.5 - 0.8 - 0.1);
  \draw[fill=black] (\posE - 0.5 + 0.9, 0.5 - 0.9) rectangle (\posE - 0.5 + 0.9 + 0.1, 0.5 - 0.9 - 0.1);

  \node[] (plus) at (6, 0){$+$};
  \node[thick, draw=black, minimum height=3cm, minimum width=1cm, fill=blue!10] (N) at (\posN, 0){};
  \node[thick, draw=black, minimum height=1cm, minimum width=2cm, fill=red!10] (F) at (\posF, 0){};
  \draw [thick] (2.25, -1.5) to [round left paren ] (2.25, 1.5);
  \draw [thick] (7.75, -1.5) to [round right paren ] (7.75, 1.5);

  \node[] (times2) at (8.5, 0){$\times$};

  \node[] (annY) at (\posY, -1.8){\scalebox{0.85}{$Y \in \mathbb{R}^{n \times d_y}$}};
  \node[] (annX) at (\posX, -1.8){\scalebox{0.85}{$X \in \mathbb{R}^{n \times d_x}$}};
  \node[] (annE) at (\posE, -1.8){\scalebox{0.85}{$E \in \mathbb{D}^{d_x \times d_x}$}};
  \node[] (annN) at (\posN, -1.8){\scalebox{0.85}{$N \in \mathbb{R}^{n \times d_x}$}};
  \node[] (annF) at (\posF, -1.8){\scalebox{0.85}{$F \in \mathbb{R}^{d_x \times d_y}$}};

  \node[] (labY) at (\posY, 2){Observations};
  \node[] (labX) at (\posX, 2){Factors};
  \node[] (labE) at (\posE, 2){Cause};
  \node[] (labE) at (\posE, 1.7){selection};
  \node[] (labN) at (\posN, 2){Noise};
  \node[] (labF) at (\posF, 2){Cause-effect};
  \node[] (labF) at (\posF, 1.7){mapping};

  \node[] (sim1) at (0,-3.25) {\scalebox{0.85}{$X \sim P(X)$}};
  \node[] (sim2) at (0,-3.65) {\scalebox{0.85}{$N \sim P(N)$}};
  \node[] (reg1) at (6,-3.25) {$\hat{E} = \text{diag}(\underbrace{(X_2^\top X_2 + \Lambda_X)^{-1} X_2^\top Y_2\overbrace{(Y_1^\top Y_1 + \Lambda_Y)^{-1} Y_1^\top X_1}^{\text{1) } \hat{X} : \text{ regression from } Y \text{ to } X}}_{\text{2) regression from } X \text{ to } \hat{X}})$};
  \end{tikzpicture}
  \caption{Back-to-back regression identifies the subset of factors $E_{ii} = 1$ in $X$ that influence some observations $Y$ by 1) regressing from $Y$ to $X$ to obtain $\hat{X}$, and 2) returning the diagonal of the regression coefficients from $X$ to $\hat{X}$.}
\label{fig:b2b}
\end{figure}

@@

\input{synthetic.tex}
\input{meg_exps.tex}

@@
